Mental Simulation as Bayesian Quadrature

### 2013-05-31 man/nips-2013.tex
Rename implementation section
Define Z

\section{Implementation}

@@

We define the prior probabilities over stimuli according to a
generative procedure. A set of $n$ vertices could be chosen in any of
$n!$ different ways, and each vertex is located at a random angle
(between 0 and $2\pi$) and radius (between 0 and 1). Thus, the prior
over a shape $X$ is $p(X)=n!\left(\frac{1}{2\pi}\right)^n$, which
gives us the denominator in Equation \ref{eq:lh-ratio}. Computing the
numerator is more difficult, as we we cannot compute $p(X_b\vert X_a,
R)$ directly. Instead, we introduce a new variable $X_R$ denoting a
mental image, which approximates $RX_a$. The $X_R$ are generated
sequentially by repeated application of a function $\tau$:
\begin{align}
  X_R=RX_a&=\tau(X_{R-r}, r)=\tau(\tau(X_{R-2r}, r), r)=\ldots{}\nonumber \\
  &=\tau^{(\frac{R}{r})}(X_a, r).
  \label{eq:tau}
\end{align} 
% I wasn't clear whether the step that happens in Equation 6 should be
% in the model, or in the algorithm. I would probably be inclined to
% define the model in full generality, and then bring up the
% increments as part of the algorithm.
Where $r$ is a small angle, and $\tau^{(i)}$ indicates $i$ recursive
applications of $\tau$. Using this sequential function, we get:
\begin{align}
  p(X_a, X_b\ \vert \ h_1)&=\int_R \int_{X} p(X_b\vert X) p(X\vert X_a, R)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  &= \int_R \int_X p(X_b\vert X)\delta(\tau^{(\frac{R}{r})}(X_a, r)-X)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  &= \int_R p(X_b\vert X_R)p(X_a)p(R)\ \mathrm{d}R
\end{align}
However, the exact form of $p(X_b\vert X_R)$ is still unknown. We
approximate it with a similarity function $S(X_b, X_R)$ which takes
into account the different possible mappings of vertices. Because the
vertices are connected in a way which forms a closed loop, we need
only consider $2n$ mappings of the $n$ vertices (we assume uncertainty
for which is the ``first'' vertex, and then which of its two neighbors
is the ``second''). So, the possible orderings are of the form
$M=\lbrace{}0, 1, \ldots{}, n\rbrace{}$, $M=\lbrace{}n, 0, \ldots{},
n-1\rbrace{}$, and so on. Combining this with a Gaussian similarity
metric, we obtain:
\begin{equation}
  S(X_b, X_R)=\frac{1}{2n}\sum_{M\in\mathbb{M}}\prod_{i=1}^n\mathcal{N}(X_b[i]\ \vert \ (MX_R)[i], \Sigma)
  \label{eq:similarity}
\end{equation}
where $i$ denotes the $i^{th}$ vertex. An example stimulus and
corresponding $S$ is shown in Figure \ref{fig:shapes}.

>>>>

\section{Metacognitive algorithms}

@@

We define the prior probabilities over stimuli according to a
generative procedure. A set of $n$ vertices could be chosen in any of
$n!$ different ways, and each vertex is located at a random angle
(between 0 and $2\pi$) and radius (between 0 and 1). Thus, the prior
over a shape $X$ is $p(X)=n!\left(\frac{1}{2\pi}\right)^n$, which
gives us the denominator in Equation \ref{eq:lh-ratio}. Computing the
numerator is more difficult, as we we cannot compute $p(X_b\vert X_a,
R)$ directly. Instead, we introduce a new variable $X_R$ denoting a
mental image, which approximates $RX_a$. The $X_R$ are generated by
repeated application of a function $\tau$:
\begin{align}
  X_R=RX_a&=\tau(X_{R-r}, r)=\tau(\tau(X_{R-2r}, r), r)=\ldots{}\nonumber \\
  &=\tau^{(\frac{R}{r})}(X_a, r).
  \label{eq:tau}
\end{align} 
where $r$ is a small angle, and $\tau^{(i)}$ indicates $i$ recursive
applications of $\tau$. Using this sequential function, we get:
\begin{align}
  p(X_a, X_b\ \vert \ h_1)&=\int_R \int_{X} p(X_b\vert X) p(X\vert X_a, R)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  &= \int_R \int_X p(X_b\vert X)\delta(\tau^{(\frac{R}{r})}(X_a, r)-X)p(X_a)p(R)\ \mathrm{d}X\ \mathrm{d}R \nonumber \\
  &= \int_R p(X_b\vert X_R)p(X_a)p(R)\ \mathrm{d}R
\end{align}
However, the exact form of $p(X_b\vert X_R)$ is still unknown. We
approximate it with a similarity function $S(X_b, X_R)$, and denote
the resulting integral as $Z$:
\begin{equation}
Z=\int_R S(X_b, X_R)p(R)\ \mathrm{d}R\approx \int_R p(X_b\vert X_R)p(R)\ \mathrm{d}R.
\label{eq:Z}
\end{equation}
We define the similarity function $S$, which incorporates the
different mappings as vertices, as follows. Because the vertices are
connected in a way which forms a closed loop, we need only consider
$2n$ mappings of the $n$ vertices (we assume uncertainty for which is
the ``first'' vertex, and then which of its two neighbors is the
``second''). So, the possible orderings are of the form $M=\lbrace{}0,
1, \ldots{}, n\rbrace{}$, $M=\lbrace{}n, 0, \ldots{}, n-1\rbrace{}$,
and so on. Combining this with a Gaussian similarity metric, we
obtain:
\begin{equation}
  S(X_b, X_R)=\frac{1}{2n}\sum_{M\in\mathbb{M}}\prod_{i=1}^n\mathcal{N}(X_b[i]\ \vert \ (MX_R)[i], \Sigma)
  \label{eq:similarity}
\end{equation}
where $i$ denotes the $i^{th}$ vertex. An example stimulus and
corresponding $S$ is shown in Figure \ref{fig:shapes}.
